\section{Introduction}
%Over the last decade how the CO2 levels have increased from 200 ppm to 400 ppm. 
%General overview of carbon emissions and climate accords.
It has come to the attention to most governmental bodies and general public that the threat of global warming is real. It is also noted that this year most countries recorded their highest ever temperature records for example, this year's July $25^{th}$ marked the hottest ever since the first recorded temperature at 1901 \cite{Pieters2019}. According to Allen et al, the $CO_2$ emissions into the atmosphere is estimated to be over 3.67 trillion tones of $CO_2$, this will cause a carbon dioxide caused warming of 2 \degree C above the pre-industrial temperatures by 2500 \cite{Allen2009}
\bigbreak
\noindent
In order to address the growing concerns of carbon emissions and global warming. The people at Zero Emission Fuels B.V (ZEF) are trying to make a micro-plant that is capable of capturing $CO_2$ from the atmosphere and converting into industry grade (AA grade) Methanol that can used as fuel or chemical feedstock. The plant is powered my Photo-voltaic Solar Energy which reduces the carbon footprint even more. The energy is utilized in the Alkaline electrolysis cell (AEC) that produces $H_2$ for reacting with $CO_2$ and making Methanol ($CH_{3}OH$) and to run the pumps and compressors across the micro-plant. 
\bigbreak
%give proper referencing here according to the section number
\noindent 
In this report we will see the scope of my internship that covers the project description. I shall also cover a section on previous work done on the Direct Air Capture system in Zero Emission Fuels B.V that laid a foundation on what I should do and on what I should improve on. I also cover what I did in the span of my internship and I have concluded the report with some remarks and suggestions for the next Direct Air Capture team of ZEF VI.   