\section*{Preface}

In this report, I have summarized the three and a half months of work I have done in Zero Emission Fuels B.V (ZEF) under the Direct Air Capture (DAC) System. The scope of my work involved the fabrication, design and controlling the DAC system as well. I have acquired new skills and learned how to use Fusion360 models for the PMMA sheets and 3D models, 3D printing using Ultimaker 3D printers for the DAC Distributor, Laser cutting of PMMA sheets for the DAC columns and Arduino coding to control the sensor systems and running the polyethylenimine (PEI) across the system. 
\bigbreak
\noindent
Zero Emission Fuels B.V is a Carbon Capture Utilization (CCU) company that manufactures a micro-plant that captures $CO_2$ using polyethylenimine (PEI) or Tetraethylenepentamine (TEPA). The captured $CO_2$ is the desorbed and separated and converted to high grade Methanol that can be used as chemical feed stock or as fuel. 
\bigbreak
\noindent
Firstly, I would like to thank the founders of ZEF B.V for the opportunity that they had given me and their constant encouragement to hustle. Mr. Hessel Jongebreur and Mr. Ulrich Starke who showed keen interest in project development and their continued enthusiasm always pushed myself. Finally, Mr. Jan van Kranendonk for his guidance throughout my internship and always gave valuable input on what to do and what not to do. 
\bigbreak
\noindent
Secondly, I would like to thank my colleagues of the ZEF V team which made it a memorable and fun working experience. I could always count on them to ask for help whenever I needed it and to improve my work. 
\bigbreak
\noindent
Thirdly, I would like to also thank my TU Delft Internship Supervisor Prof. Wiebren de Jong for his guidance and support through my Internship under ZEF and readily accepted my internship application.  
\bigbreak
\noindent
Fourthly, a special mention to the faculty of SET Internship office for giving me this opportunity and work experience. With out their work and correspondence, this internship wouldn't have been possible. Special mentions to the technicians at IO workshop for bearing my constant barging with laser cutting and 3D printing.
\bigbreak
\noindent
Finally, I would like to thank my friends, family for being understanding and supportive during my internship of these three and a half months.

\vspace{2cm}

\noindent
\textit{Nithin Jacob, \\
Delft, December, 2019}