\section{Recommendations}
\label{sec:recom}

After spending three and a half months with the ZEF B.V and the DAC system. Some of the recommendations I have for the next team and ZEF B.V in general are in the following categories. I will cover what pre requiste knowledge would have been helpful for me during my internship. Then, I will cover some of the recommendations that I have for the DAC system and finally I would like to recommend some general recommendations for the ZEF VI that I think will be useful. 

\subsection{Pre requisite knowledge}

Before starting my internship at ZEF B.V and working on the DAC system. I wish I had knew the following things before starting my internship. Knowing these things beforehand would have increased my efficiency in performing my work on the DAC system. 

\begin{itemize}
    \item \textbf{Working with chemicals: }Coming from a background of mechanical engineering in my Bachelors and having irrelevant work experience. This was my first time working with chemicals such as PEI and TEPA. This led to some haphazard and careless handling with the chemicals that were harmful. It lead to making a mess of the workspace and making undesirable spills which could have been easily avoided if I had the chemical handling training. 
    
    \item \textbf{Arduino: }I had to spend a significant time learning about electronics and arduino as I didn't have a background in it. This could have been easily avoided if I knew beforehand that I will be working with arduino for pressure, temperature, level sensors and controlling other electronics. Although there was a arduino workshop by ZEF but it was too late as we already had started working on it. 
    
    \item \textbf{ZEF inventory: }It was never clear what items were under ZEF's inventory and there was never an inventory list in which we could check. This lead to asking DEMO and Michel for a lot of stuff that had to be accounted and returned as well. If I had known about the system before working on the system, it could have saved sometime and I could have generated ideas before starting my internship itself. 
\end{itemize}

\subsection{DAC System}

On working on two DAC systems at ZEF B.V. I had learnt a thing or two about working on the system such as the below points. 

\begin{itemize}
    \item \textbf{Chemical reaction: }As covered in this report about the DAC V1.1 system failure. It had never occured to test the reaction of PEI with PLA (3D printer material). If we had done this before starting the 3D printing of the DAC V1.1 system components. We could have easily ruled it out given the chemical degradation of PLA in PEI. This could have saved time and effort for ZEF B.V. Hence, considerable thought must be given during the conceptual design. 
    
    \item \textbf{PEI and TEPA behavior: }Inorder to understand why the DAC system had been designed as such. I would have liked to know more about the polyamines used in the DAC system. 
\end{itemize}

\subsection{General recommendations}

Some general recommendations and advises that I have for the ZEF VI team is the following. 

\begin{itemize}
    \item \textbf{Not sure? Consult Jan: }Some of the errors that I had made during my internship could have been easily avoided if I had asked Jan when I wasn't sure about a process, design or anything at all. This lead to some careless mistakes that delayed the project unnecessarily. 
    
    \item \textbf{Taking delivery times into account: }We had a lot of downtime when we had to wait for the ordered parts. This lead to some downtime that I could have used for working on something else or helping in other system which in retrospect I should have done. It would have been a better utilization of my time in ZEF B.V. 
    
    \item \textbf{Writing report: }One thing I did right during my internship was writing the internship report simultaneously with the work I was doing in the internship. This lead to a detailed internship report and allowing me to work continuously on the DAC V2.0 system and the end of my internship when work was overloaded and not over working myself. I advice the further ZEFians to do the same as well.   
\end{itemize}